Monte Carlo and bootstrap for ALL parameters with tables

### 2024-09-08 Last_tables/All3_tab_algo6.Rmd
Right numbers

```{r}
# Monte carlo alone
# Number of MC iterations
B0 <- 10 # 10000 # 
```

```{r}
# Monte Carlo and bootstrap
# Number of MC iterations
B1 <- 5 # 1000 # 
# Number of bootstrap replications
B2 <- 5 # 400 # 
```

>>>>

```{r}
# Monte carlo alone
# Number of MC iterations
B0 <- 10000 # 10 # 
```

```{r}
# Monte Carlo and bootstrap
# Number of MC iterations
B1 <- 1000 # 5 # 
# Number of bootstrap replications
B2 <- 400 # 5 # 
```
